---
title: "Create Package for Stats290 Final Project"
output:
  html_document: default
---

Run this Markdown file to auto generate the R package "Stat290Pkg", which will create a new '/Stat290Pkg' directory and a Stat290Pkg_1.0.tar.gz


```{r}
installIfNeeded <- function(packages, ...) {
    toInstall <- setdiff(packages, installed.packages()[, 1])
    if (length(toInstall) > 0) {
        install.packages(toInstall, ...)
    }
}
installIfNeeded(c("devtools", "readr"))
```


## Prepare the Package##

This will overwrite the existing ones in current directory

```{r}
library(devtools)
pkgName  <- "Stat290Pkg"

## Remove any existing package named =testpack
unlink(x = "Stat290Pkg", recursive = TRUE, force = TRUE)

devtools::create(path = pkgName, rstudio = FALSE)

## Edit the DESCRIPTION file
library(readr)
descriptionFilePath <- paste(pkgName, "DESCRIPTION", sep = .Platform$file.sep)
description <- readr::read_lines(descriptionFilePath)
description[2] <- "Title: The Stat290Pkg Package"
description[3] <- "Version: 1.0"
description[5] <- paste("Description: ...")
description[7] <- "License: GPL (>= 2)"

readr::write_lines(x = description, path = descriptionFilePath)

##Indicate imports
devtools::use_package("dplyr", type = "Imports", pkg = pkgName)
devtools::use_package("readr", type = "Imports", pkg = pkgName)
#devtools::use_package("ggplot2", type = "Imports", pkg = pkgName)
#devtools::use_package("utils", type = "Imports", pkg = pkgName)
#devtools::use_package("scales", type = "Imports", pkg = pkgName)
#devtools::use_package("magrittr", type = "Imports", pkg = pkgName)
#devtools::use_package("tibble", type = "Imports", pkg = pkgName)



##
devtools::use_rcpp(pkg = pkgName)

## Save the Data
library(readr)
SFOpenData = read_csv("../data_source/Restaurant_Scores_-_LIVES_Standard.csv")
devtools::use_data(SFOpenData, pkg = pkgName)


## Document the funtion

## Write the R code back in to package:
file.copy(from = "../src/main.R",
          to = paste(pkgName, "R", "main.R", sep = .Platform$file.sep),
          overwrite = TRUE)

## Check rda data, document in bitly.R
file.info("SFOpenData")

## Document the package in Stat290Pkg.R
## Write this documented file back to /R/
file.copy(from = "Stat290Pkg.R",
          to = paste(pkgName, "R", "Stat290Pkg.R", sep = .Platform$file.sep),
          overwrite = TRUE)

## Document the data in SFOpenData.R
## Write this documented file back to /R/
file.copy(from = "SFOpenData.R",
          to = paste(pkgName, "R", "SFOpenData.R", sep = .Platform$file.sep),
          overwrite = TRUE)


## Generate the documentation under the /man directory
devtools::document(pkg = pkgName)

```


## Build the package##

```{bash}
# cd current dir
R CMD build Stat290Pkg
```

This produces the source package tar.gz.


## Check the package##

```{bash}
R CMD check Stat290Pkg_1.0.tar.gz
```



## Install the Package##


```{bash}
R CMD INSTALL Stat290Pkg_1.0.tar.gz
```

Installation worked, so let us get some info.

```{r}
packageDescription("Stat290Pkg")
```

Let us use it.

```{r}
install.packages("Stat290Pkg")
library(Stat290Pkg)
library(help = Stat290Pkg)
```

We can look up help.

```{r}
help(Stat290Pkg)
#help(function)
```

We can run the examples.

```{r}
#example(function)
```


## Session Info
```{r}
sessionInfo()
```
